UMAP reveals cryptic population structure and phenotype heterogeneity in large genomic cohorts

### 2019-06-18 ms/main.tex
add other alt HRS colouring

\begin{figure*}
    \centering
    \begin{subfigure}{\textwidth}
    \includegraphics[width=0.8\textwidth]{images/HRS_1000G_NP1_UMAP_PC7_NC2_NN15_MD05_pca_hrshisp_added1kgp_2018115153245_admix.pdf}
    \end{subfigure}
    \caption{UMAP of the first 7 principal components of the Hispanic population of the HRS, coloured by estimated admixture proportions. Admixture proportions for each individual were estimated in \cite{baharian2016great} by assuming ancestral African, Asian, and European populations using RFMIX \cite{Maples:2013fia}. We have scaled each of the three proportions to values between 0 and 255 (with 100\% corresponding to 255), to colour individual points by their estimated admixture represented by RGB where red, green, and blue respectively correspond to African, European, and Asian/Native American ancestry.}
    \label{fig:supp_umap_hrs_hisp_admix}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \begin{subfigure}{\textwidth}
    \includegraphics[width=0.8\textwidth]{images/HRS_1000G_NP1_UMAP_PC7_NC2_NN15_MD05_pca_hrshisp_added1kgp_2018115153245_admix.pdf}
    \end{subfigure}
    \caption{UMAP of the first 7 principal components of the Hispanic population of the HRS, coloured by estimated admixture proportions. Admixture proportions for each individual were estimated in \cite{baharian2016great} by assuming ancestral African, Asian, and European populations using RFMIX \cite{Maples:2013fia}. We have scaled each of the three proportions to values between 0 and 255 (with 100\% corresponding to 255), to colour individual points by their estimated admixture represented by RGB where red, green, and blue respectively correspond to African, European, and Asian/Native American ancestry. An alternate colouring is provided in figure~\ref{fig:supp_umap_hrs_hisp_admix_alt}.}
    \label{fig:supp_umap_hrs_hisp_admix}
\end{figure*}

\begin{figure*}
    \centering
    \begin{subfigure}{\textwidth}
    \includegraphics[width=0.8\textwidth]{images/HRS_1000G_NP1_UMAP_PC7_NC2_NN15_MD05_pca_hrshisp_added1kgp_2018115153245_admix132_hisp.jpeg}
    \end{subfigure}
    \caption{An alternate colouring of figure~\ref{fig:supp_umap_hrs_hisp_admix}. Here red, green, and blue correspond to African, Asian/Native American, and European ancestry, respectively.}
    \label{fig:supp_umap_hrs_hisp_admix_alt}
\end{figure*}
